Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-03-04 paper.tex
Updated figures and tables

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
\usepackage[authoryear,square]{natbib}
\usepackage{aas_macros}
\pagestyle{fancy}
\fancyhead[R]{Veibell \thepage}
\fancyhead[L]{}

\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}
\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

@@

\section{Results}

@@

\input{"tables/perltable.tex"}

@@

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
\usepackage[authoryear,square]{natbib}
\usepackage{aas_macros}
\usepackage{array}
\pagestyle{fancy}
\fancyhead[R]{Veibell \thepage}
\fancyhead[L]{}

\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}
\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

@@

\section{Results Epoch}

@@

\input{"tables/CCperltable.tex"}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[scale=0.40]{paperfigures/stormavs-mass-gt20-GOES6.eps}
\caption{$\req\ > 20~ amu/cm^3$ events from GOES6.}
\label{MassStormsGT20Figure}
\end{figure}

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{paperfigures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}
